### 2021-07-23 doc/thesis/chapters/hls.tex
one newline :)
new diagram timeline_performance_first_prototype

\includepicture [0.8] [0] {Design Time vs. Application Performance, if the same functionality is implemented in different methods for various targets \cite[Figure 1-1]{VivadoUgHLSIntro}.} {timeline_performance_first_prototype} {img/timeline_performance_first_prototype}

@@

An example for the usage of integer and fixed point data types is given in the following code section.

>>>>

\includepicture [1.0] [0] {Design Time vs. Application Performance, if the same functionality is implemented in different methods for various targets \cite[Figure 1-1]{VivadoUgHLSIntro}.} {timeline_performance_first_prototype} {img/draw.io/timeline_performance_first_prototype}

@@

An example for the usage of integer and fixed point data types is given in the following code section.\\
